---
output: 
  flexdashboard::flex_dashboard:
    theme: lumen
    favicon: ep-tab-logo.png
    vertical_layout: scroll
runtime: shiny
---

```{js gtm}
(function(w,d,s,l,i){w[l]=w[l]||[];w[l].push({'gtm.start':
new Date().getTime(),event:'gtm.js'});var f=d.getElementsByTagName(s)[0],
j=d.createElement(s),dl=l!='dataLayer'?'&l='+l:'';j.async=true;j.src=
'https://www.googletagmanager.com/gtm.js?id='+i+dl;f.parentNode.insertBefore(j,f);
})(window,document,'script','dataLayer','GTM-5L9DL97');
```


```{r global}
# print working directory for easier debugging/sanity
# via console when knitting remotely (or locally)
message(getwd()) 
#' SET MASTER PARAMETER
#' @param paramViewId a character string of the GA view
#' 
paramViewId <- "demo" # demo

# load package for custom_dollar_format
library(scales)

## set report title
report_title <- switch(paramViewId,
                       "demo" = "Article Attribution Dashboard - Example Website 1",
                       "123456" = "Article Attribution Dashboard - Example Website 2")

## set report favicon
favicon_url <- switch(paramViewId,
                      "demo" = "favicon_demo.png",
                      "123456" = "favicon_2.png")

## set custom dollar format for value box
custom_dollar_format <- switch(paramViewId,
                               "demo" = dollar_format(prefix = "$"),
                               "123456" = dollar_format(prefix = "$"))

## set custom dollar format for tables
currencyFormat <- switch(paramViewId,
                         "demo" = "$",
                         "123456" = "$")

## set logo url for inputs sidebar
logo_url <- switch(paramViewId,
                   "demo" = "ep-tab-logo-med.png",
                   "123456" = "logo_2.png")
## load packages
library(flexdashboard)
library(lubridate)
library(dplyr)
library(dygraphs)
library(xts)
library(DT)

## load source data
### GA account info for info tab
ga_account_info <- switch(paramViewId,
                          "demo" = readRDS("../data/gaAccountInfo_demo.rds"),
                          "123456" = readRDS("../data/gaAccountInfo_123456.rds"))
### GA data for summary tab
ga_data <- switch(paramViewId,
                  "demo" = readRDS("../data/viewId_demo.rds"),
                  "123456" = readRDS("../data/viewId_123456.rds"))

# keep complete cases only/remove any rows with NA to prevent Shiny load errors
# http://stackoverflow.com/questions/4862178/remove-rows-with-nas-missing-values-in-data-frame
ga_data <- ga_data[complete.cases(ga_data),]
```

---
title: `r report_title`
---

Summary {data-orientation=rows data-icon="fa-tachometer"}
=====================================  

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r inputs}
dateRangeInput(inputId = "gaDate", 
               label = "Calendar Date Range:", 
               start = max(ga_data$date)-30, 
               end = max(ga_data$date)-1, 
               min = min(ga_data$date), 
               max = max(ga_data$date), 
               format = "M d, yyyy", 
               startview = "month", 
               weekstart = 0,
               language = "en", 
               separator = " to ",
               width = NULL)

dateRangeInput(inputId = "sessionFirstArticlePublishDate", 
               label = "First Article Publish Date Range:", 
               start = min(ga_data$sessionFirstArticlePublishDate), 
               end = max(ga_data$sessionFirstArticlePublishDate),
               min = min(ga_data$sessionFirstArticlePublishDate),
               max = max(ga_data$sessionFirstArticlePublishDate), 
               format = "M d, yyyy", 
               startview = "month", 
               weekstart = 0,
               language = "en",
               separator = " to ",
               width = NULL)

selectInput(inputId = "daily_totals_metric", 
            label = "Show in Daily Totals Chart", 
            choices = c("Articles" = "articles",
                        "Sessions" = "sessions",
                        "Unique Pageviews" = "uniquePageviews",
                        "Events" = "events",
                        "Event Conversion Rate" = "eventConversionRate",
                        "Transactions" = "transactions",
                        "Conversion Rate" = "conversionRate",
                        "Revenue" = "revenue"))

## scan for url parameters on gaDate input
## so users can share links to filtered view of dashboard
observe({
      query <- parseQueryString(session$clientData$url_search)
      if (!is.null(query)) {
        updateDateRangeInput(session, 
                             "gaDate",
                             start = query[["dateFrom"]],
                             end = query[["dateTo"]])
      }
})
```

### Visit Us

- [empiricalpath.com](https://www.empiricalpath.com/?utm_source=google-cloud-platform&utm_medium=rshiny)
- [github.com/empirical-path](https://github.com/empirical-path)

### Say Hello

- [Send us an email](mailto:google.cloud@empiricalpath.com)
- [Tweet Us](https://twitter.com/empiricalpath)

```{r selected_data}
selected_data <- reactive({
  
  req(input$gaDate)
  req(input$sessionFirstArticlePublishDate)
  
  ga_data %>%  
    filter(date >= input$gaDate[1]) %>% 
    filter(date <= input$gaDate[2]) %>% 
    filter(sessionFirstArticlePublishDate >= input$sessionFirstArticlePublishDate[1]) %>% 
    filter(sessionFirstArticlePublishDate <= input$sessionFirstArticlePublishDate[2])
  
})

dailyTotalData <- reactive({
  
  req(selected_data())
  req(input$daily_totals_metric)
  
  ## transform data
  dt_ta <- selected_data() %>% 
    group_by(sessionFirstArticlePublishDate) %>% 
    summarise(articles = n_distinct(sessionFirstArticleTitle))
  
  dt_sm <- selected_data() %>% 
    group_by(date) %>% 
    summarise(uniquePageviews = sum(uniquePageviews),
                     sessions = sum(sessions),      
                     events = sum(events),
                     eventConversionRate = sum(events) / sum(sessions), 
                     transactions = sum(transactions),
                     conversionRate = sum(transactions) / sum(sessions),
                     revenue = sum(revenue))
  
  total_data <- left_join(dt_sm, dt_ta, by = c(date = "sessionFirstArticlePublishDate"))
  
  # convert to timeseries
  as.xts(total_data[input$daily_totals_metric], order.by = total_data$date) 

})
```

Row 
-----------------------------------------------------------------------

### Daily Totals

```{r dailyTotalsPlot}
renderDygraph({
  
  req(dailyTotalData())
  
  dygraph(dailyTotalData(), 
          main = paste("Total ", input$daily_totals_metric, " by Day", sep = "") ) %>%
    dySeries(input$daily_totals_metric, 
             drawPoints = TRUE, 
             label = input$daily_totals_metric) %>%
    dyHighlight(highlightCircleSize = 5)
  })
```

Row
-----------------------------------------------------------------------

### Total Articles

```{r totalArticles}
renderValueBox({
  valueBox(value = comma(length(unique(selected_data()$sessionFirstArticleTitle))),
           icon = "fa-area-chart")
})
```

### Total Unique Pageviews

```{r totalUniquePageviews}
renderValueBox({
  valueBox(value = comma(sum(selected_data()$uniquePageviews)),
           icon = "fa-area-chart")
})
```

### Total Sessions

```{r totalSessions}
renderValueBox({
  valueBox(value = comma(sum(selected_data()$sessions)),
           icon = "fa-area-chart")
})
```

### Total Events

```{r totalevents}
renderValueBox({
  valueBox(value = comma(sum(selected_data()$events)),
           icon = "fa-area-chart")
})
```

### Total Event Conversion Rate

```{r totaleventConversionRate}
renderValueBox({
  valueBox(value = percent(sum(selected_data()$events) / sum(selected_data()$sessions)),
           icon = "fa-area-chart")
})
```

### Total Transactions

```{r totaltransactions}
renderValueBox({
  valueBox(value = comma(sum(selected_data()$transactions)),
           icon = "fa-area-chart")
})
```

### Total Conversion Rate 

```{r totalconversionrate}
renderValueBox({
  valueBox(value = percent(sum(selected_data()$transactions) / sum(selected_data()$sessions)),
           icon = "fa-area-chart")
})
```

### Total Revenue

```{r totalRevenue}
renderValueBox({
  valueBox(value = custom_dollar_format(sum(selected_data()$revenue)),
           icon = "fa-area-chart")
})
```

Row {.tabset .tabset-fade data-height=1000}
-------------------------------------

### Authors

```{r tbl_arth}
selected_dataTableArth <- reactive({

  req(selected_data())
  selected_data <- selected_data()
  
  selected_data %>% 
    group_by(sessionFirstArticlePublishDate, sessionFirstArticleAuthor) %>% 
    summarise(totalArticles = length(unique(sessionFirstArticleTitle)),
              uniquePageviews = sum(uniquePageviews),
              sessions = sum(sessions),      
              events = sum(events),
              eventConversionRate = sum(events) / sum(sessions),
              transactions = sum(transactions),
              conversionRate = sum(transactions) / sum(sessions),
              revenue = sum(revenue))
})

DT::renderDataTable({
  
  req(selected_dataTableArth())
  selected_dataTableArth <- selected_dataTableArth()
  
  datatable(selected_dataTableArth,
            colnames = c("First Article Publish Date", 
                         "First Article Author", 
                         "Total Articles",
                         "Unique Pageviews", 
                         "Sessions",
                         "Events",
                         "Event Conversion Rate",
                         "Transactions",
                         "Conversion Rate",
                         "Revenue"),
            rownames = FALSE,
            filter = "top", 
            extensions = "Buttons", 
            options = list(dom = "Bltip",
                           order = list(list(9, "desc")),
                           scrollX = TRUE,
                           scrollY = "700px",
                           buttons = list(list(extend = "collection",
                                               buttons = c("csv", "excel", "pdf"),
                                               text = "Download")),
                           pageLength = 25,
                           lengthMenu = list(c(25, 50, 100, 500, -1), 
                                             c("25", "50", "100", "500", "All")))) %>%
    formatCurrency(c("revenue"), 
                   currency = currencyFormat) %>% 
    formatPercentage(c("eventConversionRate","conversionRate"), 2)
})
```

### Articles

```{r tbl_artT}
selected_dataTableArtT <- reactive({

  req(selected_data())
  selected_data <- selected_data()
  
  selected_data %>% 
    group_by(sessionFirstArticleTitle, sessionFirstArticleAuthor) %>% 
    summarise(uniquePageviews = sum(uniquePageviews),
              sessions = sum(sessions),
              events = sum(events),
              eventConversionRate = sum(events) / sum(sessions),
              transactions = sum(transactions),
              conversionRate = sum(transactions) / sum(sessions),
              revenue = sum(revenue))
})

DT::renderDataTable({
  
  req(selected_dataTableArtT())
  selected_dataTableArtT <- selected_dataTableArtT()
  
  datatable(selected_dataTableArtT,
            colnames = c("First Article", 
                         "First Article Author",
                         "Unique Pageviews",
                         "Sessions",
                         "Events",
                         "Event Conversion Rate",
                         "Transactions", 
                         "Conversion Rate", 
                         "Revenue"),
            rownames = FALSE,
            filter = "top", 
            extensions = "Buttons", 
            options = list(dom = "Bltip",
                           order = list(list(8, "desc")),
                           scrollX = TRUE,
                           scrollY = "700px",
                           buttons = list(list(extend = "collection",
                                               buttons = c("csv", "excel", "pdf"),
                                               text = "Download")),
                           pageLength = 25,
                           lengthMenu = list(c(25, 50, 100, 500, -1), 
                                             c("25", "50", "100", "500", "All")))) %>% 
    formatCurrency(c("revenue"), 
                   currency = currencyFormat) %>% 
    formatPercentage(c("eventConversionRate", "conversionRate"), 2)
})
```

### All Traffic by Date Viewed

```{r tbl_all}
selected_dataTableAll <- reactive({
  
  req(selected_data())
  selected_data <- selected_data()
  
  selected_data %>% 
    mutate(conversionRate = transactions / sessions) %>% 
    mutate(eventConversionRate = events / sessions) %>%
    select(date, 
           sessionFirstArticlePublishDate,
           sessionFirstArticleAuthor,
           sessionFirstArticleTitle,
           sessions,
           uniquePageviews,
           events,
           eventConversionRate,
           transactions, 
           conversionRate,
           revenue)
})

DT::renderDataTable({
  
  req(selected_dataTableAll())
  selected_dataTableAll <- selected_dataTableAll()
  
  datatable(selected_dataTableAll,
            colnames = c("Date", 
                         "First Article Publish Date",
                         "First Article Author", 
                         "First Article",
                         "Sessions",
                         "Unique Pageviews",
                         "Events",
                         "Event Conversion Rate",
                         "Transactions",
                         "Conversion Rate",
                         "Revenue"),
            rownames = FALSE, 
            filter = "top", 
            extensions = "Buttons", 
            options = list(dom = "Bltip",
                           order = list(list(10, "desc")),
                           scrollX = TRUE,
                           scrollY = "700px",
                           buttons = list(list(extend = "collection",
                                               buttons = c("csv", "excel", "pdf"),
                                               text = "Download")),
                           pageLength = 25,
                           lengthMenu = list(c(25, 50, 100, 500, -1), 
                                             c("25", "50", "100", "500", "All")))) %>% 
    formatCurrency(c("revenue"),
                   currency = currencyFormat) %>%
    formatPercentage(c("eventConversionRate", "conversionRate"), 2)
})
```

About This Report {data-icon="fa-info"}
=====================================     

### Overview  {data-height=200}

This report combines session and hit-level custom dimension data and allows filtering by calendar date range and the first date an article was published.

The source data of this report is exported from Google Analytics daily at 0400 EST.  

### Available Data:

**Newest Calendar Date:**  
`r max(ga_data$date)`

**Oldest Calendar Date:**  
`r min(ga_data$date)`

**Newest First Article Publish Date:**  
`r max(ga_data$sessionFirstArticlePublishDate)`

**Oldest First Article Publish Date:**  
`r min(ga_data$sessionFirstArticlePublishDate)`

### Google Analytics Account Info

```{r gaAccountInfo}
DT::renderDataTable({
  datatable(ga_account_info,
            rownames = FALSE,
            extensions = "Buttons",
            options = list(
              dom = "t"))
})
```

### How to Use {data-height=200}

1. Select calendar date range
2. Select article publish date 
3. Select a metric to display in the daily time series chart from the "Show in Daily Totals Chart" dropdown 
4. Gain insights! 
5. Use the "Download button at top of "All" table to export data currently visible

### Source Code {data-height=100 data-icon="fa-code-fork"}

- GitHub Repository [repo-name](https://github.com/empirical-path/)

Contact Us {data-icon="fa-envelope"}
=====================================     

#### Email Us:

- **General Support:** [google.cloud@empiricalpath.com](mailto:google.cloud@empiricalpath.com)
- **Developer Support:** [Justin Marciszewski](mailto:google.cloud@empiricalpath.com)
