---
output: 
  flexdashboard::flex_dashboard:
    theme: lumen
    favicon: ep-tab-logo.png
    vertical_layout: scroll
runtime: shiny
---

```{js gtm}
(function(w,d,s,l,i){w[l]=w[l]||[];w[l].push({'gtm.start':
new Date().getTime(),event:'gtm.js'});var f=d.getElementsByTagName(s)[0],
j=d.createElement(s),dl=l!='dataLayer'?'&l='+l:'';j.async=true;j.src=
'https://www.googletagmanager.com/gtm.js?id='+i+dl;f.parentNode.insertBefore(j,f);
})(window,document,'script','dataLayer','GTM-5L9DL97');
```


```{r global}
#' SET MASTER PARAMETER
#' @param paramViewId a character string of the GA view
#' 
paramViewId <- "demo" # demo

#' LOAD REMAINING PARAMETERS
#' @param filepath
#' 
#' @return sourceData
#' @return report_title
#' @return favicon_url
#' 
# source("../config.R")

library(scales)

## set report title
report_title <- switch(paramViewId,
                       "demo" = "Article Attribution Report - Example Website 1",
                       "123456" = "Article Attribution Report - Example Website 2")

## set report favicon
favicon_url <- switch(paramViewId,
                      "demo" = "favicon_demo.png",
                      "123456" = "favicon_2.png")

# load GA account info
# ga_account_info <- switch(paramViewId,
#                           "demo" = readRDS("../../data/gaAccountInfo_demo.rds"),
#                           "123456" = readRDS("../../data/gaAccountInfo_123456.rds"))

# set custom dollar format for value box
custom_dollar_format <- switch(paramViewId,
                               "demo" = dollar_format(prefix = "$"),
                               "123456" = dollar_format(prefix = "$"))

# set custom dollar format for tables
currencyFormat <- switch(paramViewId,
                         "demo" = "$",
                         "123456" = "$")

# set logo url for inputs sidebar
logo_url <- switch(paramViewId,
                  "demo" = "ep-tab-logo-med.png",
                   "123456" = "logo_2.png")

                   

## load packages
library(flexdashboard)
library(lubridate)
library(dplyr)
library(dygraphs)
library(xts)
library(DT)

## load source data
sourceData <- switch(paramViewId,
                     "demo" = readRDS("../data/viewId_demo.rds"), 
                     "123456" = readRDS("../data/viewId_123456.rds"))

# keep complete cases only/remove any rows with NA to prevent Shiny load errors
# http://stackoverflow.com/questions/4862178/remove-rows-with-nas-missing-values-in-data-frame
sourceData <- sourceData[complete.cases(sourceData),]
```

---
title: `r report_title`
---

Summary {data-orientation=rows}
=====================================  

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r inputs}
dateRangeInput(inputId = "gaDate", 
               label = "Calendar Date Range:", 
               start = max(sourceData$date)-30, 
               end = max(sourceData$date)-1, 
               min = min(sourceData$date), 
               max = max(sourceData$date), 
               format = "M d, yyyy", 
               startview = "month", 
               weekstart = 0,
               language = "en", 
               separator = " to ",
               width = NULL)

dateRangeInput(inputId = "sessionFirstArticlePublishDate", 
               label = "First Article Publish Date Range:", 
               start = min(sourceData$sessionFirstArticlePublishDate), 
               end = max(sourceData$sessionFirstArticlePublishDate),
               min = min(sourceData$sessionFirstArticlePublishDate),
               max = max(sourceData$sessionFirstArticlePublishDate), 
               format = "M d, yyyy", 
               startview = "month", 
               weekstart = 0,
               language = "en",
               separator = " to ",
               width = NULL)

selectInput(inputId = "daily_totals_metric", 
            label = "Show in Daily Totals Chart", 
            choices = c("Articles" = "articles",
                        "Sessions" = "sessions",
                        "Unique Pageviews" = "uniquePageviews",
                        "Events" = "events",
                        "Event Conversion Rate" = "eventConversionRate",
                        "Transactions" = "transactions",
                        "Conversion Rate" = "conversionRate",
                        "Revenue" = "revenue")
            )

# scan for url parameters on calendar date range or gaDate input
observe({
      
      query <- parseQueryString(session$clientData$url_search)
      
      if (!is.null(query)) {
        updateDateRangeInput(session, 
                             "gaDate",
                             start = query[["dateFrom"]],
                             end = query[["dateTo"]])
      }
})
```

```{r selectedData}
selectedData <- reactive({
  req(input$gaDate)
  req(input$sessionFirstArticlePublishDate)
  
  sourceData %>%  
    dplyr::filter(date >= input$gaDate[1]) %>% 
    dplyr::filter(date <= input$gaDate[2]) %>% 
    dplyr::filter(sessionFirstArticlePublishDate >= input$sessionFirstArticlePublishDate[1]) %>% 
    dplyr::filter(sessionFirstArticlePublishDate <= input$sessionFirstArticlePublishDate[2])
  
})

dailyTotalData <- reactive({
  
  req(selectedData())
  req(input$daily_totals_metric)
  
  selectedData <- selectedData()
  
  ## transform data
  dt_ta <- selectedData %>% 
    dplyr::group_by(sessionFirstArticlePublishDate) %>% 
    dplyr::summarise(articles = n_distinct(sessionFirstArticleTitle))
  
  dt_sm <- selectedData %>% 
    dplyr::group_by(date) %>% 
    dplyr::summarise(
      uniquePageviews = sum(uniquePageviews),
      sessions = sum(sessions),      
      events = sum(events),
      eventConversionRate = sum(events) / sum(sessions), 
      transactions = sum(transactions),
      conversionRate = sum(transactions) / sum(sessions),
      revenue = sum(revenue)
    )
  
  total_data <- left_join(dt_sm, dt_ta, by = c(date = "sessionFirstArticlePublishDate"))
  
  # convert to timeseries
  as.xts(total_data[input$daily_totals_metric], order.by = total_data$date) 

})
```

![](`r logo_url`)

Row 
-----------------------------------------------------------------------

### Daily Totals

```{r dailyTotalsPlot}
renderDygraph({
  req(dailyTotalData())
  
  ts_data <- dailyTotalData()
  
    d <- dygraph(ts_data, 
                 main = paste("Total ", input$daily_totals_metric, " by Day", sep = "") ) %>%
      dySeries(input$daily_totals_metric, 
               drawPoints = TRUE, 
               label = input$daily_totals_metric) %>%
      dyHighlight(highlightCircleSize = 5)    
    
    d

  })
```

Row
-----------------------------------------------------------------------

### Total Articles

```{r totalArticles}
renderValueBox({
  valueBox(
    value = comma(length(unique(selectedData()$sessionFirstArticleTitle))),
    icon = "fa-area-chart"
  )
})
```

### Total Unique Pageviews

```{r totalUniquePageviews}
renderValueBox({
  valueBox(
    value = comma(sum(selectedData()$uniquePageviews)),
    icon = "fa-area-chart"
  )
})
```

### Total Sessions

```{r totalSessions}
renderValueBox({
  valueBox(
    value = comma(sum(selectedData()$sessions)),
    icon = "fa-area-chart"
  )
})
```

### Total Events

```{r totalevents}
renderValueBox({
  valueBox(
    value = comma(sum(selectedData()$events)),
    icon = "fa-area-chart"
  )
})
```

### Total Event Conversion Rate

```{r totaleventConversionRate}
renderValueBox({
  valueBox(
    value = percent(sum(selectedData()$events) / sum(selectedData()$sessions)),
    icon = "fa-area-chart"
  )
})
```

### Total Transactions

```{r totaltransactions}
renderValueBox({
  valueBox(
    value = comma(sum(selectedData()$transactions)),
    icon = "fa-area-chart"
  )
})
```

### Total Conversion Rate 

```{r totalconversionrate}
renderValueBox({
  valueBox(
    value = percent(sum(selectedData()$transactions) / sum(selectedData()$sessions)),
    icon = "fa-area-chart"
  )
})
```

### Total Revenue

```{r totalRevenue}
renderValueBox({
  valueBox(
    value = custom_dollar_format(sum(selectedData()$revenue)),
    icon = "fa-area-chart"
  )
})
```

Row {.tabset .tabset-fade data-height=1000}
-------------------------------------

### Authors

```{r tbl_arth}
selectedDataTableArth <- reactive({

  req(selectedData())
  selectedData <- selectedData()
  
  selectedData %>% 
    group_by(sessionFirstArticlePublishDate, sessionFirstArticleAuthor) %>% 
    summarise(
      totalArticles = length(unique(sessionFirstArticleTitle)),
      uniquePageviews = sum(uniquePageviews),
      sessions = sum(sessions),      
      events = sum(events),
      eventConversionRate = sum(events) / sum(sessions),
      transactions = sum(transactions),
      conversionRate = sum(transactions) / sum(sessions),
      revenue = sum(revenue) 
    )
  
})

DT::renderDataTable({
  req(selectedDataTableArth())
  selectedDataTableArth <- selectedDataTableArth()
  
  datatable(selectedDataTableArth,
            colnames = c("First Article Publish Date", 
                         "First Article Author", 
                         "Total Articles",
                         "Unique Pageviews", 
                         "Sessions",
                         "Events",
                         "Event Conversion Rate",
                         "Transactions",
                         "Conversion Rate",
                         "Revenue"),
            rownames = FALSE,
            filter = "top", 
            extensions = "Buttons", 
            options = list(dom = "Bltip",
                           order = list(list(9, "desc")),
                           scrollX = TRUE,
                           scrollY = "700px",
                           buttons = list(list(extend = "collection",
                                               buttons = c("csv", "excel", "pdf"),
                                               text = "Download")),
                           pageLength = 25,
                           lengthMenu = list(c(25, 50, 100, 500, -1), 
                                             c("25", "50", "100", "500", "All")))) %>%
    formatCurrency(c("revenue"), 
                   currency = currencyFormat) %>% 
    formatPercentage(c("eventConversionRate","conversionRate"), 2)
})
```

### Articles

```{r tbl_artT}
selectedDataTableArtT <- reactive({

  req(selectedData())
  selectedData <- selectedData()
  
  selectedData %>% 
    group_by(sessionFirstArticleTitle, sessionFirstArticleAuthor) %>% 
    summarise(
      uniquePageviews = sum(uniquePageviews),
                      sessions = sum(sessions),
                      events = sum(events),
                      eventConversionRate = sum(events) / sum(sessions),
                      transactions = sum(transactions),
                      conversionRate = sum(transactions) / sum(sessions),
                      revenue = sum(revenue)
    )
    
})

DT::renderDataTable({
  req(selectedDataTableArtT())
  selectedDataTableArtT <- selectedDataTableArtT()
  
  datatable(selectedDataTableArtT,
            colnames = c("First Article", 
              "First Article Author",
              "Unique Pageviews",
              "Sessions",
              "Events",
              "Event Conversion Rate",
              "Transactions", 
              "Conversion Rate", 
              "Revenue"),
            rownames = FALSE,
            filter = "top", 
            extensions = "Buttons", 
            options = list(dom = "Bltip",
                           order = list(list(8, "desc")),
                           scrollX = TRUE,
                           scrollY = "700px",
                           buttons = list(list(extend = "collection",
                                               buttons = c("csv", "excel", "pdf"),
                                               text = "Download")),
                           pageLength = 25,
                           lengthMenu = list(c(25, 50, 100, 500, -1), 
                                             c("25", "50", "100", "500", "All")))) %>% 
    formatCurrency(c("revenue"), 
                   currency = currencyFormat) %>% 
    formatPercentage(c("eventConversionRate", "conversionRate"), 2)
})
```

### All Traffic by Date Viewed

```{r tbl_all}
selectedDataTableAll <- reactive({
  req(selectedData())
  selectedData <- selectedData()
  
  selectedData %>% 
    mutate(conversionRate = transactions / sessions) %>% 
    mutate(eventConversionRate = events / sessions) %>%
    select(date, 
           sessionFirstArticlePublishDate,
           sessionFirstArticleAuthor,
           sessionFirstArticleTitle,
           sessions,
           uniquePageviews,
           events,
           eventConversionRate,
           transactions, 
           conversionRate,
           revenue)
})

DT::renderDataTable({
  req(selectedDataTableAll())
  selectedDataTableAll <- selectedDataTableAll()
  
  datatable(selectedDataTableAll,
            colnames = c("Date", 
                         "First Article Publish Date",
                         "First Article Author", 
                         "First Article",
                         "Sessions",
                         "Unique Pageviews",
                         "Events",
                         "Event Conversion Rate",
                         "Transactions",
                         "Conversion Rate",
                         "Revenue"),
            rownames = FALSE, 
            filter = "top", 
            extensions = "Buttons", 
            options = list(dom = "Bltip",
                           order = list(list(10, "desc")),
                           scrollX = TRUE,
                           scrollY = "700px",
                           buttons = list(list(extend = "collection",
                                               buttons = c("csv", "excel", "pdf"),
                                               text = "Download")),
                           pageLength = 25,
                           lengthMenu = list(c(25, 50, 100, 500, -1), 
                                             c("25", "50", "100", "500", "All")))) %>% 
    formatCurrency(c("revenue"),
                   currency = currencyFormat) %>%
    formatPercentage(c("eventConversionRate", "conversionRate"), 2)
})
```

Source Data Info
=====================================     

### Available Data:

**Newest Calendar Date:**  
`r max(sourceData$date)`

**Oldest Calendar Date:**  
`r min(sourceData$date)`

**Newest First Article Publish Date:**  
`r max(sourceData$sessionFirstArticlePublishDate)`

**Oldest First Article Publish Date:**  
`r min(sourceData$sessionFirstArticlePublishDate)`

### Google Analytics 360 Account Info

```{r gaAccountInfo}
# DT::renderDataTable({
#   datatable(ga_account_info,
#             rownames = FALSE,
#             extensions = "Buttons", 
#             options = list(
#               dom = "t")
#             )
# })
```

About This Report
=====================================     

### Overview  {data-height=200}

This report combines session and hit-level custom dimension data and allows filtering by calendar date range and the first date an article was published.

The source data of this report is exported from Google Analytics daily at 0400 EST.  

Please see the [Source Data Info](#section-source-data-info) tab for full details of the data available.

### How to Use {data-height=200}

1. Select calendar date range
2. Select article publish date 
3. Select a metric to display in the daily time series chart from the "Show in Daily Totals Chart" dropdown 
4. Gain insights! 
5. Use the "Download button at top of "All" table to export data currently visible

### Source Code {data-height=100}

- GitHub Repository [repo-name](https://github.com/empirical-path/)

Get Help
=====================================     

#### Email Us:

- **Developer Support:** [Justin Marciszewski](mailto:justin@empiricalpath.com)
- **General Support:** [google.cloud@empiricalpath.com](mailto:google.cloud@empiricalpath.com)

